Machine Learning Working Notes

### 2017-09-03 ml_notes/draft.tex
- add ansible and vagrant files
repo clean

\author{
	Huang Xiao\thanks{Visiting homepage: feuerchop.github.io} \\
	Department of Computer Science\\
	Technical University of Munich\\
	Munich, Germany 85748 \\
%	\texttt{hippo@cs.cranberry-lemon.edu} \\
%	\And
%	Coauthor \\
%	Affiliation \\
%	Address \\
%	\texttt{email} \\
%	\AND
%	Coauthor \\
%	Affiliation \\
%	Address \\
%	\texttt{email} \\
%	\And
%	Coauthor \\
%	Affiliation \\
%	Address \\
%	\texttt{email} \\
%	\And
%	Coauthor \\
%	Affiliation \\
%	Address \\
%	\texttt{email} \\
%	(if needed)\\
}

@@

\end{abstract}
\section{Linear Models}
\subsection{Regression}
It seems everything starts to grow from linear model, whatever regression or classification, linear models expand to almost many other learning models we face during the research. So starting from a very simple linear regression problem, given training set $\set D = \left\{ \vct x_i, \vct y_i \right\}_{i=1}^n $ with $ n $ sample, where $ \vct y $ are the responses as numerical values. A linear regression model finds a linear weight vector, which minimizes a certain type of empirical error. This is obviously defined in perspective of statistical learning theory. 
\begin{equation}
\argmin_{\vct w} \frac{1}{n}\sum_{i=1}^n \| w^T x_i + b - y_i\|^2
\end{equation}
where empirical error introduced by individual sample is equally weighted by $ 1/n $. It is seen that we are using a straight line to fit a possibly any shaped function, obviously the summation or mean error can be large due to the noise or intrinsic nonlinearity of function. However, a typical misunderstanding of linear model for beginners is that the term linear refers to $ \vct w $ instead of $ \vct x $. That is to say, we are expecting a linear model on parameters $ \vct w $, but the feature vectors $ \vct x $ can actually be any shape. Therefore, in literature we mostly see a feature mapping of input $ \vct x $ as $ \phi(\vct x) $, and it does not break the linear property of the model. Therefore, we have our liner model as,
\begin{equation}
\argmin_{\vct w} \frac{1}{n}\sum_{i=1}^n \| w^T \phi(x_i) + b - y_i\|^2
\label{eq:linear_reg}
\end{equation}
A typical feature mapping is polynomial feature mapping. Suppose we have a 2-dimensional input data sample $ \left( x_1, x_2 \right) $, we define a feature mapping as follows,
\[ \left( x_1, x_2 \right) \rightarrow \left( x_1, x_2, x_1^2+x_2^2 \right)\], where a 2-d plane is transformed as a paraboloid in 3-d space. Substituting back into previous linear function, it becomes a polynomial line fitting problem, but it is still linear in $ \vct w $.

@@

\bibliography{myrefs}
\bibliographystyle{icml2016}

>>>>

\author{
	Huang Xiao\thanks{Website: www.huangxiao.de} \\
	Department of Computer Science\\
	Technical University of Munich\\
	Munich, Germany 85748 \\
%	\texttt{hippo@cs.cranberry-lemon.edu} \\
%	\And
%	Coauthor \\
%	Affiliation \\
%	Address \\
%	\texttt{email} \\
%	\AND
%	Coauthor \\
%	Affiliation \\
%	Address \\
%	\texttt{email} \\
%	\And
%	Coauthor \\
%	Affiliation \\
%	Address \\
%	\texttt{email} \\
%	\And
%	Coauthor \\
%	Affiliation \\
%	Address \\
%	\texttt{email} \\
%	(if needed)\\
}

@@

\end{abstract}
\section{Linear Models}
\subsection{Regression}
It seems everything starts to grow from linear model, whatever regression or classification, linear models expand to almost many other learning models we face during the research. So starting from a very simple linear regression problem, given training set $\set D = \left\{ \vct x_i, \vct y_i \right\}_{i=1}^n $ with $ n $ sample, where $ \vct y $ are the responses as numerical values. A linear regression model finds a linear weight vector, which minimizes a certain type of empirical error. This is obviously defined in perspective of statistical learning theory. 
\begin{equation}
\argmin_{\vct w} \frac{1}{n}\sum_{i=1}^n \| w^T x_i + b - y_i\|^2
\end{equation}
where empirical error introduced by individual sample is equally weighted by $ 1/n $. It is seen that we are using a straight line to fit a possibly any shaped function, obviously the summation or mean error can be large due to the noise or intrinsic nonlinearity of function. However, a typical misunderstanding of linear model for beginners is that the term linear refers to $ \vct w $ instead of $ \vct x $. That is to say, we are expecting a linear model on parameters $ \vct w $, but the feature vectors $ \vct x $ can actually be any shape. Therefore, in literature we mostly see a feature mapping of input $ \vct x $ as $ \phi(\vct x) $, and it does not break the linear property of the model. Therefore, we have our liner model as,
\begin{equation}
\argmin_{\vct w} \frac{1}{n}\sum_{i=1}^n \| w^T \phi(x_i) + b - y_i\|^2
\label{eq:linear_reg}
\end{equation}
A typical feature mapping is polynomial feature mapping. Suppose we have a 2-dimensional input data sample $ \left( x_1, x_2 \right) $, we define a feature mapping as follows,
\[ \left( x_1, x_2 \right) \rightarrow \left( x_1, x_2, x_1^2+x_2^2 \right), \] where a 2-d plane is transformed as a paraboloid in 3-d space. Substituting back into previous linear function, it becomes a polynomial line fitting problem, but it is still linear in $ \vct w $.

@@

\section{Anomaly Detection: A Survey}
In this section, I review literatures of importance in regard of anomaly detection in recent years, a more thorough survey of this research domain can be found also in \cite{Hodge2004, Chandola2009}.

\section{Supervised Sequence Labeling}
The problem of supervised sequence labeling \cite{Graves2013} is to assign a sequence of labels given an input sequence. Suppose we have input sequence of length $ m $: $ \vct x_i = \left\lbrace x_i^{0}, x_i^{1}, \ldots, x_i^{m}\right\rbrace $, we aim to learn a function which assigns a sequence of labels $ \vct t_i $ of length $ s $ on $ \vct x_i $. That is, 
\begin{align*}
& f(x_i)  = \vct t_i, \\
\text{where} \quad & \vct t_i = \left\lbrace t_i^{0}, t_i^{1}, \ldots, t_i^{s}\right\rbrace
\end{align*}                 
For supervised sequence labeling, there's training labels available and accordingly there're
typically three types of learning tasks in sequence labeling.

\begin{description}
	\item[Sequence Classification] 
	It seeks a discriminative classification function to assign 
	singular label to a whole input sequence. This is a \textit{m-vs-1} relationship.
	For instances, a sentence type classifier automatically assigns a sentence to a type
	label. \textit{Who is president of USA?} is a \textit{question} sentence.

	Error function for sequence classification can be as easy as normal binary or multiclass
	classification problem, e.g., using softmax cross entropy to measure the loss.

	\item[Segment Classification] 
	Different from sequence classification, segment classifcation generates a shorter sequence 
	of labels that are assigned to segments of sequence. This is a \textit{m-vs-s} relationship.
	Namely we have $ | \vct t_i | < | \vct x_i |$. This is analog to image segmenation which 
	learns to segment image to different objects.

	Error function for segment classification can be set as percentage of misclassified segments.
	Denote the a test sequence dataset $S' = \left\lbrace (\vct x_i, \vct z_i)_{i=1}^N \right\rbrace$,
	and a segment classification function $h(\cdot)$, the segment error can be defined as, 
	\[
		E^{seg}(h, S') = \frac{1}{Z}\sum_{(x,z)\in S'} \text{HD}(h(x), z),
	\]
	where \textbf{HD} is the hamming distance between two equal length sequences.

	\item[Temporal Classification] 
	Temporal classification is a \textit{N-vs-N} relationship. Each step of input sequence 
	generates a output label, it turns out the output length shall be equal to input sequence
	length.

	A simple error function can be defined as edit distance of two sequences, namely the minimal
	number of \textit{insertions, substitutions and deletions}. 
	\[
		E^{Temp}(h, S') = \frac{1}{Z}\sum_{(x,z)\in S'} \text{ED}(h(x), z),
	\]
	where \textbf{ED} is edit distance.

\end{description}

\bibliography{myrefs}
\bibliographystyle{plain}
\bibliographystyle{icml2016}
